### 2016-08-22 doc/publications/plos16/plos16.tex
small changes to paper

\end{flushleft}
% Please keep the abstract below 300 words
\tableofcontents
\clearpage
\section{Notes}
\begin{itemize}
\item   I think the structure of the first section should be
  \begin{itemize}
  \item  convergence results from Biau 2012
  \item consider  \cite{Segal.2004} examples
  \item simulations reproduced from Genuer et al 2010 (no -- we need classification examples)
  \item check Piotr's simulation
  \item run sparkML or Cursed forest on the  simulation data 
  \item we extend the simulations to many more variables 
  \item I dont think I can get R to handle chromosme 1 etc. May have to run CF on chromosme 22, see table
    \ref{table:smaller_data} -- On it, Aidan
  \item variable  selection may succeed where accurate prediction does not
  \item discussion of the effect of the ntree and mtry parameters for variable selection with many noise variables
  \item   perhaps we argue that in the case where the relationship of $X$ and $y$ takes a particular form (step, ramp) we can recover
    the significant variables in the presence of a very large number of noise variables
  \item in the case of genomic data, our functions of interest are more likely to be stop or ramp functions rather than harmonic
    functions. So we have some hope.
  \end{itemize}
\item check out 
  \begin{itemize}
  \item D\'iaz-Uriarte, R., \& Alvarez de Andr\'es, S. (2006). (done)
  \item Goldstein et al. (2011)
  \item Chen (2012)  (done)
  \item VSURF and  varSelRF, (doee) recursive feature (forwards backwards) using variable importance
  \item ranger package
  \item  r2VIM: A new variable selection method for random forests in
    genome-wide association studies
  \item CloudForest: A Scalable and Efficient Random Forest Implementation for Biological Data
  \item \cite{Tuv.et.al.2009} feature selection via adding permuted variables. Do we want to consider this? (no, leave it for now)
  \end{itemize}
\item other things to do
  \begin{itemize}
  \item what is the problem with bagging? Do we need to redo the thousand genome stuff?
  \end{itemize}
\end{itemize}

>>>>

\end{flushleft}
% Please keep the abstract below 300 words
\tableofcontents
\clearpage
\section{Notes}
\begin{itemize}
\item   I think the structure of the first section should be
  \begin{itemize}
  \item  convergence results from Biau 2012  (done)
  \item consider  \cite{Segal.2004} examples
  \item simulations reproduced from Genuer et al 2010 (no -- we need classification examples)
  \item check Piotr's simulation  (done)
  \item run sparkML or Cursed forest on the  simulation data 
  \item we extend the simulations to many more variables 
  \item I dont think I can get R to handle chromosme 1 etc. May have to run CF on chromosme 22, see table
    \ref{table:smaller_data} -- On it, Aidan
  \item variable  selection may succeed where accurate prediction does not
  \item discussion of the effect of the ntree and mtry parameters for variable selection with many noise variables
  \item   perhaps we argue that in the case where the relationship of $X$ and $y$ takes a particular form (step, ramp) we can recover
    the significant variables in the presence of a very large number of noise variables
  \item in the case of genomic data, our functions of interest are more likely to be stop or ramp functions rather than harmonic
    functions. So we have some hope.
  \end{itemize}
\item check out 
  \begin{itemize}
  \item D\'iaz-Uriarte, R., \& Alvarez de Andr\'es, S. (2006). (done)
  \item \cite{Goldstein.et.al.2011}
notes that the 0, 1, 2 encoding of alleles is an additive model i.e. each additional minor allele increases the effect 
\begin{verbatim}
Different genetic effects
Type	Mechanism	Partition
Additive	Each additional minor allele increases variation	0, 1, 2
Dominant	Presence of at least 1 minor allele increases variation	0, 1/2
Recessive	Two minor alleles needed for variation	0/1, 2
Heterosis	Heterozygote leads to variation	0/2, 1
\end{verbatim}

  \item Chen (2012)  (done)
  \item VSURF and  varSelRF, (doee) recursive feature (forwards backwards) using variable importance
  \item ranger package
  \item  r2VIM: A new variable selection method for random forests in
    genome-wide association studies
  \item CloudForest: A Scalable and Efficient Random Forest Implementation for Biological Data
  \item \cite{Tuv.et.al.2009} feature selection via adding permuted variables. Do we want to consider this? (no, leave it for now)
  \end{itemize}
\item other things to do
  \begin{itemize}
  \item what is the problem with bagging? Do we need to redo the thousand genome stuff?
  \end{itemize}
\end{itemize}
